Think deep for reef resilience

### 2025-09-10 paper/paper_draft.qmd
Change the plotting framework for carbonate budgets and add to paper doc

Reef median depth had a moderate positive correlation with the number of years a reef
maintains coral cover above the assumed carbonate budget threshold required to sustain live
coral cover ($\theta_{0}$). Greater median depth was a key characteristic defining reefs
that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate;
@sfig-access-esm1-5-mean-carb-budget). Unsurprisingly, the number of years above $\theta_0$
substantially decreased as $\theta_0$ is increased, as does the Spearman's correlation.
Decreasing correlation levels are likely due to an increasing number of reefs being unable
to maintain coral cover above $\theta_0$ as it is increased, with the distribution of years
above threshold becoming increasingly right-skewed
(@fig-access-esm1-5-depth-conn-carbonate). In contrast, weighted incoming connectivity
strength (Log-10 scale) was found to have no correlation with the number of years a reef
maintains cover above the required thresholds (@fig-access-esm1-5-depth-conn-carbonate).

![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075
(y-axis). The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef variables (depth -
left and Log-10 weighted incoming connectivity - right) and the number of years cover
exceeds the carbonate budget threshold. Point colour represents the median reef depth in
metres in the left-hand panel, and Log-10 weighted incoming connectivity in the right-hand
panel. Red points represent the mean number of years above an assumed carbonate budget
threshold across reefs. Deeper reefs are better able to maintain cover above the indicative
carbonate budget threshold, while there is no considerable relationship between weighted
incoming connectivity and carbonate budget maintenance. Displays results from median time
series using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
fig-align="center" width="14.82cm"}

@@

![Scatter plot indicating reef median depth (metres) and Log10 weighted incoming
connectivity for each reef. Point colours represent the mean number of years each reef
maintains positive carbonate budgets across each $theta$ value from 10-20% live coral cover.
Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget
fig-align="center" width="10cm"}

>>>>

Reef median depth had a moderate positive correlation with the number of years a reef
maintains coral cover above the assumed carbonate budget threshold required to sustain live
coral cover ($\theta_{0}$). Greater median depth was a key characteristic defining reefs
that sustain coral cover above $\theta_{0}$ (@fig-access-esm1-5-depth-conn-carbonate;
@sfig-access-esm1-5-mean-carb-budget; @sfig-access-esm1-5-carb-budget-corr). Unsurprisingly,
the number of years above $\theta_0$ substantially decreased as $\theta_0$ is increased, as
does the Spearman's correlation (@sfig-access-esm1-5-carb-budget-corr). Decreasing
correlation levels are likely due to an increasing number of reefs being unable to maintain
coral cover above $\theta_0$ as it is increased, with the distribution of years above
threshold becoming increasingly right-skewed (@fig-access-esm1-5-depth-conn-carbonate). In
contrast, weighted incoming connectivity strength (Log-10 scale) was found to have no
correlation with the number of years a reef maintains cover above the required thresholds
(@fig-access-esm1-5-carb-budget-corr).

![Number of years reef coral cover exceeds the carbonate budget threshold from 2025 to 2075
(y-axis) and reef median depth (left panel) and reef Log10 weighted incoming connectivity
values (right panel). Point colour represents the threshold assessment values used to assess
positive carbonate budget status ($\theta_0$). Deeper reefs are better able to maintain
cover above the indicative carbonate budget threshold, while there is no considerable
relationship between weighted incoming connectivity and carbonate budget maintenance.
Displays results from median time series using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_comparison.png){#fig-access-esm1-5-depth-conn-carbonate
fig-align="center" width="14.82cm"}

@@

![Bar plot indicating the Spearman's rank correlation values for the number of years above
carbonate budget threshold and, median reef depth and Log10 weighted incoming connectivity
values. Depth correlation values are displayed in the left plot, while connectivity
correlation values are displayed in the right plot. Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/depth_conn_carbonate_correlations.png){#sfig-access-esm1-5-carb-budget-corr
fig-align="center" width="14.82cm"}

![Scatter plot indicating reef median depth (metres) and Log10 weighted incoming
connectivity for each reef. Point colours represent the median number of years each reef
maintains positive carbonate budgets across each $theta$ value from 10-20% live coral cover.
Displays results for ACCESS-ESM1-5
GCM.](../figs/ACCESS-ESM1-5/depth_conn_mean_carbonate_budget.png){#sfig-access-esm1-5-mean-carb-budget
fig-align="center" width="14.82cm"}
